\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.6in,top=0.6in]{geometry}
    \usepackage[colorlinks=true,linkcolor=black,urlcolor=black]{hyperref}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}



%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Kevin Rodríguez Rodríguez}}\\
	\vspace*{2pt}
	{\large Software Engineer}\\
	\vspace*{2pt}
	Bogotá D.C, Colombia $\cdot$ kyrodriguez97@gmail.com $\cdot$ +57 310 338 0312 $\cdot$ \url{https://kevyder.dev/}\\
\end{center}

%==== Summary ====%
\header{Summary}
\vspace{1mm}
Backend-focused Software Engineer with 9+ years of experience building and shipping production web applications and APIs in Python (Django, FastAPI) and Ruby on Rails. Over the last year, focused on full-stack delivery (Vue/Nuxt, TypeScript) and AI/LLM-powered features (RAG, LangChain, vector databases). Comfortable owning a project end-to-end, from requirements through cloud deployment.

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{Freelance} \hfill Remote\\
\textit{Software Engineer} \hfill September 2025 - Present\\
\vspace{-2mm}
\begin{itemize} \itemsep 0pt
	\item Development and deployment of full-stack web applications using Python (FastAPI/Django) and Vue.js (Nuxt).
	\item Developed type-safe frontend components and modules utilizing TypeScript.
	\item Built LLM-powered features using RAG, LangChain, the OpenAI SDK, and vector databases.
	\item Designed and integrated RESTful APIs to connect backend services with responsive user interfaces.
	\item Managed end-to-end project lifecycles, from requirement gathering to cloud deployment.
	\item Optimized application performance and implemented best practices for clean, maintainable code.
\end{itemize}
\vspace*{-1mm}
\textbf{Simetrik} \hfill Bogotá D.C - Colombia, Remote\\
\textit{Backend Developer} \hfill May 2024 - May 2025\\
\vspace{-2mm}
\begin{itemize} \itemsep 0pt
	\item Microservice development with Python, FastAPI, PostgreSQL and AWS, improving service efficiency and reducing response latency across core endpoints.
	\item Development of Python Unit Test
	\item Implemented continuous integration for automated testing of codebase.
	\item Conducted code reviews
	\item Participated in agile development sprints to deliver features on time.
\end{itemize}
\textbf{Freelance / Independent Projects} \hfill Remote\\
\textit{Software Engineer} \hfill July 2023 - May 2024\\
\vspace{-2mm}
\begin{itemize} \itemsep 0pt
	\item Designed and delivered backend solutions for independent clients using Python (Django/FastAPI), managing project lifecycles end-to-end.
\end{itemize}
\vspace{-2mm}
\vspace*{-1mm}
\textbf{KLYM} \hfill Bogotá D.C - Colombia, Remote\\
\textit{Backend Engineer} \hfill February 2023 - July 2023\\
\vspace{-2mm}
\begin{itemize} \itemsep 0pt
	\item Python and Django applications support and development.
	\item Collaborated with cross-functional teams to define project requirements.
	\item Developed and executed pytest tests for Python and Django applications.
	\item Implemented continuous integration for automated testing of codebase.
	\item Conducted code reviews
	\item Participated in agile development sprints to deliver features on time.
\end{itemize}
\textbf{Freelance / Independent Projects} \hfill Remote\\
\textit{Software Engineer} \hfill July 2022 - February 2023\\
\vspace{-2mm}
\begin{itemize} \itemsep 0pt
	\item Designed and delivered backend solutions for independent clients using Python (Django/FastAPI), managing project lifecycles end-to-end.
\end{itemize}
\vspace{-2mm}
\vspace*{-1mm}
\textbf{Elenas} \hfill Bogotá D.C - Colombia, Remote\\
\textit{Backend Engineer} \hfill October 2020 - July 2022\\
\vspace{-2mm}
\begin{itemize} \itemsep 0pt
	\item Django framework development and support for GraphQL API systems.
	\item Implemented security best practices to safeguard sensitive data.
	\item Collaborated with the QA team to conduct thorough testing of backend systems.
	\item Developed and executed pytest tests for Python and Django applications.
	\item Implemented continuous integration for automated testing of codebase.
	\item Conducted code reviews and mentored a team of 3-5 junior developers.
	\item Participated in agile development sprints to deliver features on time.
	\item Collaborated with front-end developers to integrate user-facing elements.
\end{itemize}
\vspace*{-1mm}
\textbf{Omnilatam/Greensill Latam} \hfill Bogotá D.C - Colombia\\
\textit{Backend Engineer} \hfill August 2019 - October 2020\\
\vspace{-2mm}
\begin{itemize} \itemsep 0pt
	\item Ruby on Rails, Python, Django, and Airflow software development.
	\item Designed and implemented scalable backend solutions for business applications.
	\item Created scraping workflows with Ruby on Rails and Airflow (Python)
	\item Participated in agile development sprints to deliver features on time.
\end{itemize}
\vspace*{-1mm}
\textbf{Earlier Experience} \hfill Bogotá D.C - Colombia\\
\textit{Web Developer / Programmer — DesignPlus, Serdan, Samtel} \hfill June 2015 - May 2019\\
\vspace{-2mm}
\begin{itemize} \itemsep 0pt
	\item Built and maintained web applications using Ruby on Rails, PHP, jQuery, HTML/CSS, and VB6 across three roles.
	\item Participated in the full software development lifecycle, from requirements to deployment and support.
	\item Conducted code reviews and collaborated with cross-functional teams to ship features on schedule.
\end{itemize}

%==== Education ====%
\header{Education}
\textbf{SENA}\hfill Bogotá D.C - Colombia\\
Technologist ADSI \hfill January 2014 - December 2016\\
\vspace{1mm}
\textbf{UNINPAHU}\hfill Bogotá D.C - Colombia\\
Degree in Software Engineering \hfill January 2017 - June 2019\\
\vspace{1mm}

\header{Skills}
\textbf{Languages:} Python, TypeScript, JavaScript, Ruby \\
\textbf{Backend Frameworks:} Django, Django REST Framework, FastAPI, Flask, Ruby on Rails \\
\textbf{Frontend:} Vue.js, Nuxt \\
\textbf{AI / LLM:} LangChain, OpenAI SDK, RAG, Vector Databases (Qdrant) \\
\textbf{Databases:} PostgreSQL, Vector Databases \\
\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, Git \\
\textbf{Testing:} pytest, Unit Testing \\
\textbf{Practices:} REST APIs, GraphQL, Agile/Scrum, Code Review \\
\vspace{1mm}

\header{PROJECTS}
{\textbf{Constitución Colombia Chat}} {\sl Python, Streamlit, Qdrant, OpenAI, RAG, LangChain} \hfill \url{https://constitucion91.kevyder.dev/}\\
A Streamlit RAG chat over the Constitución Política de Colombia de 1991\\
\vspace*{1mm}
{\textbf{palabrandom}} {\sl Typescript, Nuxthub, Cloudflare D1} \hfill \url{https://palabrandom.com/}\\
A simple web app that generates random English/Spanish words for vocabulary practice\\
\vspace*{1mm}
{\textbf{Banrepco - MCP server}} {\sl FastAPI, Docker, Typescript} \hfill \url{https://github.com/kevyder/banrepco_mcp}\\
An MCP server that exposes data from Colombia's central bank, such as inflation and exchange rates.\\
\vspace*{1mm}

\header{MORE ABOUT ME}
\textbf{LinkedIn:} \url{https://www.linkedin.com/in/kevin-rodriguez-software-engineer}\\
\textbf{Github:} \url{https://github.com/kevyder}\\
\textbf{Website:} \url{https://kevyder.dev/}\\

\end{document}
